\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-01-10 presentations/popl19-01-2019/presentation.tex
Add POPL19 definition evaluation slide

>>>>

\begin{frame}
  \frametitle{Evaluating the definition}
  \begin{enumerate}
  \item {\itshape Intuitive}\\
    \onslide<2->{Yes, call stack corresponds exactly to our intuition.}
\item {\itshape Useful for reasoning}\\% we should be able to use WBCF and LSE
                                % when reasoning about correctness and security
                                % of programs using \stktokens{}.
  \onslide<3->{Yes, ...}
\item {\itshape Reusable in secure compiler chains}\\% for compilers using \stktokens{}, one should be able to rely on WBCF and LSE when proving correctness and security of other compiler passes and then compose such results with ours to obtain results about the full compiler.
  \onslide<4->{Yes, fully-abstract compilations compose vertically, so oLCM can
    be used as a target for other compilation phases.}
\item {\itshape Arguably "complete"}\\% the formalization should arguably capture the entire meaning of WBCF and LSE and should arguably be applicable to any reasonable program. 
  \onslide<5->{Yes, ...}
%\item {\itshape potentially scalable}% although dynamic code generation and multi-threading are currently out of scope, the formalization should, at least potentially, extend to such settings.
\end{enumerate}
\end{frame}
